Current State of Knowledge Representation Systems for Robotics

### 2011-12-08 krs-survey.tex
Added references to Chen (WrightEagle team), Vincze, Lozano-Perez

@@

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\hiderowcolors
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model} & {\bf Reasoner} & Main reference \\
\hline
\showrowcolors
{\sc KnowRob} & KRS & Tenorth (TU Munich) & \url{http://ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & KRS & Lemaignan \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
GSM & & Mavridis, Roy \par (MIT MediaLab) & & & & & \cite{Mavridis2006} \\
OMKRF & & Suh et al. \par (Hanyang Univ.) & & & & & \cite{Suh2007} \\
DY-KNOW & & Heintz, Dowerty \par (Linköping Univ.) & & & & & \cite{Heintz2004} \\
 & & Wrighteagle \\
 & & Vincze \\
ARMAR & & Schmidt-Rohr (Karlsruhe TH) \\
 & & Hertzberg (Osnabrück Univ.) \\
 & & (DFKI Bremen) \\
 (based on {\sc KnowRob} & & (JSK) \\

@@

This section tries to summary the various approaches we surveyed in the
previous section.  This summary does not exactly follow the list of compared
features presented in section~\ref{sect|compared-features}. We have organized
it along four axis: \emph{what can be represented?}, \emph{How knowledge is
created and grounded?}, \emph{What can be done with the knowledge?} and
\emph{How to use knowledge in the whole, larger robot architecture?}.

@@

>>>>

\fxnote{Should we also mention the general dynamics of the knowledge representation system? ie, the
system from the point of view of an on-going cognitive process. See \cite{Henderson2011}}

@@

%\begin{tabularx}{\textheight}{p{2cm}p{4cm}p{3cm}p{4cm}p{2.3cm}p{2cm}p{2cm}}
\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{2.8cm}p{1.5cm}}
\hiderowcolors
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model} & {\bf Reasoner} & Main reference \\
\hline
\showrowcolors
{\sc KnowRob} & KRS & Tenorth, Beetz \par (TU Munich) & \url{http://ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL & Custom \par ({\sc Prolog}) & \cite{Tenorth2009a} \\
ORO & KRS & Lemaignan, Alami \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) & {\sc Pellet} & \cite{Lemaignan2010} \\
PEIS KR\&R & KRS & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & & \cite{Daoutis2009} \\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & & \cite{Jacobsson2008} \\
Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & & \cite{Sabri2011} \\
GSM & & Mavridis, Roy \par (MIT MediaLab) & & & & & \cite{Mavridis2006} \\
OMKRF & & Suh et al. \par (Hanyang Univ.) & & & & & \cite{Suh2007} \\
DY-KNOW & & Heintz, Dowerty \par (Linköping Univ.) & & & & & \cite{Heintz2004} \\
Ke Jia & & Chen et al. \par (Univ. of Science and Technology of China) & & & & & \cite{Chen2010} \\
 & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\
 & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\
ARMAR & & Schmidt-Rohr (Karlsruhe TH) \\
 & & Hertzberg (Osnabrück Univ.) \\
 & & (DFKI Bremen) \\
 (based on {\sc KnowRob} & & (JSK) \\

@@

This section tries to summary the various approaches we surveyed in the
previous section.  This summary does not exactly follow the list of compared
features presented in section~\ref{sect|features}. We have organized
it along four axis: \emph{what can be represented?}, \emph{How knowledge is
created and grounded?}, \emph{What can be done with the knowledge?} and
\emph{How to use knowledge in the whole, larger robot architecture?}.

@@

\fxnote{Mention symmetry and research of invariants \cite{Henderson2011} as a process to create knowledge?}
